---
title: "Rmarkdown Template"
output:
  html_document:
    fig_caption: yes
    theme: flatly
    toc: yes
    toc_depth: 3
    toc_float: yes
---

1.  Fork this repository and give it your own name
2.  Create a new R project from version control using the URL from your newly created (forked) repository.

# YAML Settungs {#section-1}

> global markdown options here



# Section 2 (basic formatting) {#section-2 .tabset}

## Text formatting

*italic* or **bold** `code` superscript^2^ and subscript~2~

## Lists

-   Bulleted list item 1

-   Item 2

    -   Item 2a

    -   Item 2b

1.  Numbered list item 1

2.  Item 2. The numbers are incremented automatically in the output.

## Tables

> Creating tables by hand.

| First Header | Second Header |
|--------------|---------------|
| Content Cell | Content Cell  |
| Content Cell | Content Cell  |

# Section 3 (not sure yet) {#section-3}

# Section 4 (figure captions) {#section-4}

------------------------------------------------------------------------

Specify the caption of your figure in the chunk header. Example:

```{r, eval=FALSE}
{r, fig.align="center", fig.width=6, fig.height=6, fig.cap="Figure: Here is a really important caption."}
```

```{r, message=FALSE, warning=FALSE, fig.align="center", fig.width=6, fig.height=6, fig.cap="Figure: Here is a really important caption."}
library(tidyverse)
mpg %>%
  ggplot( aes(x=reorder(class, hwy), y=hwy, fill=class)) + 
    geom_boxplot() +
    xlab("class") +
    theme(legend.position="none")
```
